---
title: "Linux"
output: 
  xaringan::moon_reader:
    seal: false
    libs: libs
    css: ["css/xaringan.css", "default", "default-fonts"]
    nature:
      ratio: '16:9'
      # beforeInit: ["addons/macros.js", "https://platform.twitter.com/widgets.js"]
      highlightLines: true
      highlightSpans: false
      highlightStyle: github
      countIncrementalSlides: false
      countdown: false
      slideNumberFormat: '%current%'
      navigation:
        scroll: false
editor_options: 
  chunk_output_type: console
---

class: inverse, middle, center

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.duplicate.label = "allow")
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
```


class: inverse, middle, center

<br>

# .orange[Introduction to `UNIX`/`Linux` and `Bash` Scripting]

### Deepak Kumar Tanwar

#### Bioinformatics Specialist and Trainer<br>Swiss Institute of Bioinformatics<br>University of Zurich

### `r anicon::faa("envelope", animate="", colour = "#2395fb")` [.red1[deepak.tanwar@uzh.ch]](mailto:deepak.tanwar@uzh.ch)<br> `r anicon::faa("envelope", animate="", colour = "#2395fb")` [.red1[deepak.tanwar@sib.swiss]](mailto:deepak.tanwar@sib.swiss)

### `r fontawesome::fa("bluesky",fill =  "#00acee")` [.red1[@dktanwar.bsky.social]](https://bsky.app/profile/dktanwar.bsky.social)

---


```{r child='p1.Rmd'}
```

---

```{r child='p2.Rmd'}
```   

<!-- --- -->

<!-- ```{r child='p3.Rmd'} -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r child='p4.Rmd'} -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r child='p5.Rmd'} -->
<!-- ``` -->

<!-- --- -->

<!-- ```{r child='p6.Rmd'} -->
<!-- ``` -->

---

class: center, middle, hide_logo

.eLarge[.blue[**Thank you for your attention!**]]
